---
title: "Investment Report"
output: 
  html_document:
    toc: true
    code_folding: hide
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
date: "`r format(Sys.time(), '%d %B %Y')`"
editor_options: 
  chunk_output_type: console
---

<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
h1.title {
  color: #F08080;
  background-color: #F5F5F5;
  opacity: 0.6;
  font-family: Calibri;
  font-size: 20px;
}
h4.author {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
  background-color: #F5F5F5;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

## Introduction

The goal of this project is to predict de novo, the biological age of the normal and healthy colon samples in the DNA methylation dataset from the [genomicClass](https://github.com/genomicsclass/coloncancermeth/blob/master/data/coloncancermeth.rda) github page. The CpGs that determine the biological clock will be the predictors. A CpG is a C, followed by a G but from the  $5^1$ end to the  $3^1$ end of a DNA strand.

Epigenetic mechanisms regulate gene expression. Certain technologies enable us measure some epigentic endpoints. One example is DNA methylation. DNA methylation is a chemical process that occurs around genes and which is capable of silencing gene expression. In this project, I will analyse DNA methylation data for the whole genome and relate it to phenotypic variation.

It has been studied that when part of a genome is methylated, the gene close to it is not expressed. It is inherited at mitosis. Methylation often occurs at CpG islands.

When one DNA strand is methylated, so is the other. If we also have a CpG on one strand, we have it as well on the other strand.When DNA replicates, its methylation characteristics are preserved.

## Load the libraries

```{r}
## load packages
library(ggplot2)
library(IRanges)
library(S4Vectors)
```

## Mile stones
### Loading the data

```{r}

```

